### 2015-05-13 Draft/background.tex
Added Related Gabel and Su in Related work
Cleaned Related Work and Background

Closes #3

%Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
%However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
%These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.

%In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are leveraged in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state-of-the-art approaches have demonstrated to be effective in classifying POS tags for well-written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking further enhances the syntax of a sentence in addition to POS tagging. Current state-of-the-art approaches can effectively classify phrases and clauses over well-written news articles.

\textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}. The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. It provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.

@@

We next present SE specific NLP techniques.

@@

\textbf{Programming keywords}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However POS tagging works satisfactorily on well-written news articles which does not necessary entail that the tagging works satisfactorily on domain-specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

@@

Noun boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation assists the POS tagger to accurately annotate the POS tags of the words thus increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.

\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:

@@

\item \textbf{Period Handling}. Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

\item \textbf{Named Entity Handling}. Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
Further resolution of these phrases using grammatical syntax is unnecessary and would not bring forth any semantic value.
Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
This heuristic annotates the phrase representing the name of the entities as a single lexical token.

\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations interleaved with text.
This interleaving may result in POS tagger to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator from semantically annotated sentences. 
The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

In next section we describe our generic approach to infer temporal constraints from API documents.

>>>>

We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are leveraged in this work.

@@

\textit{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}: Also known as \textit{`word tagging'} and \textit{`grammatical tagging'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to.

\textit{Phrase and Clause Parsing}: Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking further enhances the syntax of a sentence in addition to POS tagging.

\textit{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.

@@

%We next present SE specific NLP techniques.

@@

\textit{Programming Keywords}~\cite{pandita12:inferring}: Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However POS tagging developed for well written news articles, often performs unsatisfactorily on domain-specific text.
In particular, with respect to API documents certain words have a different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

@@

Noun boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation directs the POS tagger to correctly annotate the POS tags of the domain specific words thus increasing accuracy of subsequent NLP techniques such as chunking and typed dependency annotation.

\textit{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
%These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.

@@

\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

\item \textit{Named Entity Handling}: Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
Further resolution of such phrases using grammatical syntax may not bring forth any semantic value.
Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
This heuristic annotates the phrase representing the name of the entities as a single lexical token.

\item \textit{Abbreviation Handling}: Natural-language sentences often consist of abbreviations interleaved with text.
This interleaving may result in POS tagger to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

@@

\textit{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}:
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) like representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this representation, by constructing an intermediate representation generator from semantically annotated sentences. 
The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

### 2015-05-13 Draft/introduction.tex
ASE Changes
Added Related Gabel and Su in Related work
Cleaned Related Work and Background

Closes #3

Application Programming Interfaces (APIs) facilitates software reuse
by providing standardized mechanism to access API components.
However, an API has some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use. % and may even result in financial losses.

@@

The rest of the paper is organized as follows.
Section~\ref{sec:example} presents a real-world example that motivates our approach.
Section~\ref{sec:related} discusses related work.
Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
Section~\ref{sec:approach} presents our approach.
Section~\ref{sec:evaluation} presents the evaluation of our approach.
Section~\ref{sec:discussion} presents brief discussion on the limitations and future work.
Finally, Section~\ref{sec:conclusion} concludes.

>>>>

Application Programming Interfaces (APIs) facilitate software reuse
by providing standardized mechanism to access API components.
However, an API has some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use. % and may even result in financial losses.

@@

%The rest of the paper is organized as follows.
%Section~\ref{sec:example} presents a real-world example that motivates our approach.
%Section~\ref{sec:related} discusses related work.
%Section~\ref{sec:background} presents the  background on NLP techniques used in our approach.
%Section~\ref{sec:approach} presents our approach.
%Section~\ref{sec:evaluation} presents the evaluation of our approach.
%Section~\ref{sec:discussion} presents brief discussion on the limitations and future work.
%Finally, Section~\ref{sec:conclusion} concludes.

### 2015-05-13 Draft/related.tex
Added Related Gabel and Su in Related work
Cleaned Related Work and Background

Closes #3

Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries. In contrast, \tool\ infers specifications from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.

@@

\textbf{Augmented Documentation}:
Improving the documentation related to a software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, \tool\ both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

>>>>

Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries. 
Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
\textit{micropatterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
In contrast, \tool\ infers specifications from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.

@@

\textbf{Augmented Documentation}:
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the Eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, \tool\ both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
